\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-06 manuscript/main.tex
update the result

In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}. To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio. The index is to measure the effects of Lianjia's operations and its continuous expansion. The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets. This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables. The DBI is calculated as follows:

@@

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DiD) estimation to estimate the offline's store's entry's influence on the market performance. From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood. Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets. Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics. Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales. However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period. Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.1\% increase in the first post-entry period. Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$. This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.

In terms of the transaction period, the offline store's influence is always not significant, which suggests that the offline store's entry does not help to match the buyers and sellers in searching the houses, which is in line with the intuition that when platform is more mature, people's searching behavior is more likely to be online. Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect. This suggests that the presence of offline stores may facilitate an increase in price concessions. This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations. Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.

@@

% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

@@

The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction number did not show a statistically significant difference. However, after the first year, the transaction number demonstrated a significant positive increase, ranging from 2.9\% to 6.2\%. Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion. However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year. However, the effect becomes insignificant after the third year.

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings.

@@

In this paper, we demonstrated that in China's real estate market, brokerage offline stores play a critical role in transactions. Brokerages can adopt offline store expansion strategies to gain significant benefits. Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%. Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, it facilitates better communication between buyers and sellers. % this is wrong

Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by X% to Y% and boost the number of viewings by X% to Y%. However, this effect does not significantly impact communication, thus not affecting the price adjustment range or transaction cycle.

Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength. The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.

%首先，我们的结果表明链家的门店扩张会导致链家在该地区的说如提高\%到\%，并会导致带看次数也就是吸引客人的数量增加\%到%，此外，研究表明线下门店扩张效应对于成交周期并没有显著影响，但是可以帮助买卖双方扩大信息的沟通，从而减少调价幅度。第二，链家的platform-mediated consolidation同样可以提高链家的成交收入在%到%，并会导致带看次数增加%到%，但是该效应并不会对人们的沟通产生影响，从而影响调价幅度和成交周期。最后，我们建立局部网络效应并且我们发现链家的网络效应主要是局部clustering的并且网络强度是moderate的，链家的platform-mediated consolidation可以帮助链家获得更大的局部网络效应，这将帮助链家在长期获得更大的影响力。

Our research has several implications. Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies. This shift underscores the need for firms to enhance their digital strategies to remain competitive. Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering. For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.

This exercise is also of broad implications The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}.

@@

The study of Lianjia's strategic expansion into China's real estate brokerage industry, particularly through the implementation of the ACN and the proliferation of offline branches, underscores a transformative impact on market dynamics and transaction efficiency. Our empirical research shows that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior, particularly through improved price concessions and increased home viewing. The study highlights the critical role of offline store information and community proximity in increasing transaction revenue and achieving market dominance, even in the face of increasing monopolization trends. Despite the adverse effects of the COVID-19 pandemic, which temporarily diluted the benefits of both customer base expansion and information dissemination, the resilience of physical stores emerges prominently. This resilience, coupled with the strategic leverage of online platforms, underscores the importance of a synergistic online-offline model in overcoming market challenges and maintaining competitive advantage. The findings argue for a nuanced understanding of platform-based monopolization in real estate, suggesting that the successful integration of digital and physical domains can significantly enhance service delivery, market penetration, and overall system competitiveness, paving the way for a more adaptive and robust market system in the face of evolving challenges.

>>>>

In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}. To take the natural logarithm without lossing information, we decided to add one to the number of house tours because some transactions are purely online-based. Additionally, we decided to winsorize the sample for the natural logarithms of Lianjia's transaction number, home tours, and transaction period at the 1st and 99th percentiles to mitigate the influence of extreme values. The price concession is defined as $|\frac{\text{transaction price} - \text{listing price}}{\text{listing price}}| \times 100\%$. To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio. The index is to measure the effects of Lianjia's operations and its continuous expansion. The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets. This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables. The DBI is calculated as follows:

@@

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DID) estimation to estimate the offline's store's entry's influence on the market performance. From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood. Although Lianjia's entry is not a randomized event, the DiD estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets. Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that there is no anticipation effect for Lianjia's entry. In terms of the Lianjia's entry effect ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales. However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period. Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.1\% increase in the first post-entry period. Nonetheless, this effect diminishes in the second post-treatment period ($post_2$), though it continues to exhibit statistical significance in the third post-treatment period ($post_3$). % This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.

Regarding the transaction period, the influence of the offline store is consistently insignificant. This finding suggests that the entry of offline stores does not facilitate the matching of buyers and sellers in the housing market. This outcome aligns with the intuition that when platform and online information is readily accessible, individuals' search behavior tends to be predominantly online-based. Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect. This suggests that the presence of offline stores may facilitate an increase in price concessions. This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations. Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.

@@

We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_entry}. For this test, we employed a neighborhood sample with randomly generated treatment effects. Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects. The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

@@

The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction number did not show a statistically significant difference. However, after the first year, the transaction number demonstrated a significant positive increase, ranging from 2.9\% to 6.2\%. Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of consolidation over traditional offline expansion. However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year. However, the effect becomes insignificant after the third year.

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_platform} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis.

@@

Our study highlights the transformative impact of Lianjia's strategic expansion in China's real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches. Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours. Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%. Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, but it facilitates better communication between buyers and sellers by contributing the price concession in transaction. Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by 2.9\% to 6.2\% and boost the number of house tours by 2.9\% to 3.0\%. However, this effect does not significantly impact communication, thus not affecting the price concession and transaction period. Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength. The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.

Our research has several implications. Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies. This shift underscores the need for firms to enhance their digital strategies to remain competitive. Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering. For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform. Lastly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency. These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}.

@@

Future research could explore several potential directions. First, investigating the long-term impacts of online and offline integration on market competition and consumer behavior in various real estate markets globally could provide comparative insights. Second, examining the role of emerging technologies, such as artificial intelligence and blockchain, in further enhancing the efficiency and transparency of real estate transactions would be valuable. Third, assessing the socio-economic implications of platform-based monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications. Lastly, exploring the adaptability of the online-offline integration model in other sectors, such as healthcare and education, could extend the applicability of these findings and contribute to a broader understanding of digital transformation across industries.
